% !TEX root = ../dissertation.tex

% title
\title{Analysis of Process Criticality Accident Risk Using a \texorpdfstring{\\}{} Metamodel-Driven Bayesian Network}

% author
\author{William John Zywiec}

% previous degrees
\bsdepartment{Nuclear Engineering}
\bsschool{Rensselaer Polytechnic Institute}
\bsgrad{May 2013}

\msdepartment{Systems Engineering}
\msschool{The Johns Hopkins University}
\msgrad{May 2017}
\showmsdegree
% \hidemsdegree

% PhD degree commands
% committee
\showcommitteepage
% \hidecommitteepage 
\committee{
  Shahram Sarkani, Professor, Dissertation Director\\\\
  Thomas Andrew Mazzuchi, Professor, Dissertation Co-Director}

% chair must be entered separately for formatting reasons
\chair{Shahram Sarkani}
\chairtitle{Professor}
\cochair{Thomas Andrew Mazzuchi}
\cochairtitle{Professor}
\department{Engineering Management and Systems Engineering}

\phdgrad{November X, 2020}
\defensedate{November X, 2020}
% year of completion for copyright page
\year=2020

% copyright page
% \copyrightholder{someone else}

% dedication
\dedication{
  \begin{center}
    For my family.
  \end{center}}

% acknowledgments
\acknowledgments{
  I would like to thank my wife, Katrina, for supporting me throughout my undergraduate and graduate education, and for going along with my decision to pursue a PhD.
  I would also like to thank my advisors, Dr. Shahram Sarkani and Dr. Thomas Mazzuchi, for providing invaluable advice and guidance, and for putting together and managing an excellent program.
  Additional thanks go to Daniel Falbel, for answering questions about \textit{TensorFlow}, and Dr. Shankar Kulumani, for putting together the \LaTeX\ template I used to write this dissertation.
  Lastly, I would like to thank David Heinrichs and Dr. Thomas McLaughlin, because "if I have seen further it is by standing on the shoulders of giants."}

% choose preface, prologue, or foreword

% preface
\preface{}

% prologue
\prologue{}

% foreword
\foreword[2]{}

% show/hide front matter pages
\showcopyright
\showabstract
\showcommitteepage
\showdedication
\showacknowledgments
\hidepreface
\hideprologue
\hideforeword

% table of contents
% show/hide lists of figures, tables, etc.
\showlistoffigures
\showlistoftables
\hidenomenclature 
\hidelistofabbreviations
\hidelistofsymbols

% the glossaries package automatically turns off lists of abbreviations and symbols
\setabbreviationstyle[acronym]{long-short}
\setabbreviationstyle[abbreviation]{long-short}
\makeglossaries

% show/hide the glossaries page
\showglossarieslistofabbreviations
\hideglossarieslistofsymbols
\hideglossariesglossaryofterms

\loadglsentries{tex/glossaries-abbreviations.tex}
% \loadglsentries{tex/glossaries-symbols.tex}
% \loadglsentries{tex/glossaries-terms.tex}

% abstract
\abstract{
  Since the discovery of fission in 1938, there have been more than 60 criticality accidents throughout the world.
  These accidents are divided into two categories: those that occur during critical experiments or operations with research reactors, and those that occur in production facilities, more commonly referred to as \textit{process criticality accidents}.
  The focus of this work is on the development of a methodology that uses a Bayesian network and a neural network metamodel to estimate process criticality accident risk.}
